\documentclass[10pt,letterpaper]{article}

\usepackage[margin=0.52in]{geometry}
\usepackage[T1]{fontenc}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{titlesec}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{3pt}
\setlist[itemize]{leftmargin=0.18in, itemsep=2pt, topsep=2pt}

\titleformat{\section}
  {\large\bfseries}
  {}
  {0pt}
  {}
  [\titlerule]
\titlespacing*{\section}{0pt}{7pt}{4pt}

\newcommand{\resumeRole}[4]{
  \textbf{#1} \hfill #2 \\
  #3 \hfill #4
}

\newcommand{\resumeProject}[3]{
  \textbf{#1} \textbar{} #2 \hfill #3
}

\begin{document}

\begin{center}
{\Large \textbf{SARVESH GANESAN}}\\
India \textbar{} +91 8668063705 \textbar{} \href{mailto:sarveshganesan2002@gmail.com}{sarveshganesan2002@gmail.com} \textbar{}
\href{https://linkedin.com/in/sarvesh-ganesan09}{linkedin.com/in/sarvesh-ganesan09} \textbar{}
\href{https://github.com/Sarvesh-GanesanW}{github.com/Sarvesh-GanesanW}
\end{center}

\section*{Professional Summary}
Lead AI Architect with 2.5+ years of experience building and shipping a cloud-native enterprise data platform from the ground up. Major architect of 12+ production microservices spanning agentic AI, distributed ETL, data lakehousing, and MLOps, all running on AWS EKS. Proven track record of turning ambiguous product requirements into scalable, cost-optimized systems that serve real enterprise workloads.

\section*{Technical Skills}
\begin{itemize}
  \item \textbf{Languages \& Frameworks:} Python, FastAPI, Flask, REST APIs, gRPC, SSE streaming
  \item \textbf{AI / LLM:} AWS Bedrock, Strands Agents, LangChain, LangGraph, RAG systems, MCP
  \item \textbf{Data Engineering:} Apache Spark, Apache Iceberg, DuckDB, Pandas, PyArrow, Polars
  \item \textbf{Databases:} PostgreSQL, pgvector, Redis, Pinecone, MongoDB, Elasticsearch, DynamoDB
  \item \textbf{Cloud \& Infra:} AWS (EKS, Bedrock, S3, Lambda, ECR, CloudWatch), Docker, Kubernetes, Karpenter
  \item \textbf{MLOps:} MLflow, Jupyter, PyTorch, TensorFlow, scikit-learn, Docker-based GPU runtimes
\end{itemize}

\section*{Experience}
\resumeRole{Lead AI Architect}{Sep 2023 -- Mar 2026}{Groundzero Software Private Limited}{Chennai, India}
\begin{itemize}
  \item Owned the entire backend architecture end-to-end, designing and shipping 12+ production microservices for agentic chat, data providers, ETL orchestration, Iceberg lakehouse APIs, MLOps, and Spark/DuckDB runtimes as the sole backend engineer.
  \item Built a multi-agent AI system that lets enterprise users query databases, build dashboards, run ETL jobs, and manage notebooks through natural language, reducing time-to-insight from hours of manual work to seconds of conversation.
  \item Scaled data connectivity to 69+ sources through a dynamically loaded connector architecture with role-based authorization and schema introspection caching.
  \item Reduced RAG query latency by 90\% using hybrid vector plus full-text retrieval with neural reranking, enabling real-time document Q\&A at production scale.
  \item Delivered sub-10s query performance on 100M+ row datasets by architecting a TB-scale Apache Iceberg lakehouse with Spark and DuckDB compute engines.
  \item Cut LLM inference costs with three-tier model routing, Anthropic prompt caching, and per-request token tracking across agent workflows.
  \item Designed the ETL orchestration layer for job submission, multi-job chaining, container log streaming from EKS pods, and dataset lineage across Spark, DuckDB, and Pandas engines.
  \item Stood up MLOps and platform infrastructure with MLflow, Jupyter lifecycle management on EKS, GPU training containers, Karpenter autoscaling, and 99.9\% uptime across multi-tenant deployments.
\end{itemize}

\resumeRole{Software Trainee}{Jun 2023 -- Aug 2023}{SCI-BI Software Solutions Private Limited}{Chennai, India}
\begin{itemize}
  \item Built client-facing dashboards and reports in Power BI and Tableau, and translated client requirements into technical specifications.
\end{itemize}

\section*{Projects}
\resumeProject{SRE Tea MCP Server}{Node.js, Model Context Protocol, Claude, JWT, AWS Lambda}{\href{https://github.com/Sarvesh-GanesanW/sre-tea-mcp}{GitHub}}
\begin{itemize}
  \item Built a production MCP server for live tea e-commerce administration, exposing 46 tools across orders, products, customers, inventory, invoices, logistics, churn analytics, and reporting with automatic token refresh and parallel API aggregation.
  \item Integrated Claude Desktop, Claude Code, and custom MCP clients over STDIO transport with secure environment-based credentials, structured stderr logging, and automatic recovery from expired JWT sessions.
\end{itemize}

\resumeProject{Qualipilot Data Quality Checker}{Python, Polars, Dask, cuDF, AWS Bedrock}{\href{https://github.com/Sarvesh-GanesanW/dataqualitychecker}{GitHub}}
\begin{itemize}
  \item Built a production data-quality CLI/library with missing, duplicate, type, range, outlier, cardinality, and freshness checks, CI severity gates, HTML/JSON/Markdown reports, and optional LLM narration through Bedrock, Ollama, or OpenAI-compatible endpoints.
  \item Implemented swappable Polars, Pandas, Dask, and cuDF engines with typed Pydantic results, deterministic JSON output, Docker/Lambda deployment paths, and probabilistic record linkage for deduplication.
\end{itemize}

\resumeProject{PlannerAgent}{LangGraph, Anthropic, AWS Bedrock, Python}{\href{https://github.com/Sarvesh-GanesanW/PlannerAgent}{GitHub}}
\begin{itemize}
  \item Built a conversational planning agent supporting 10+ turn dialogues, clarifying questions, persistent compressed sessions, versioned plans, 12+ templates, Gantt charts, and Trello/CSV/Markdown import/export.
  \item Implemented explicit LangGraph state flow, context compaction near token limits, pickle+gzip session storage, undo/redo history, provider switching across Anthropic and Bedrock, and 40+ tests.
\end{itemize}

\section*{Education}
\textbf{Bachelor of Technology: Computer Science and Engineering} \hfill May 2023\\
Specialization in Artificial Intelligence and Machine Learning \hfill GPA: 9.08\\
SRM Institute of Science and Technology, Chennai

\section*{Languages}
English (Fluent) \textbar{} Tamil (Native) \textbar{} Telugu (Fluent) \textbar{} Hindi (Intermediate)

\end{document}
